Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex
paper: modifiche all'ultima figura

\begin{figure*}[h!]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3 loss} & {\sc synthetic 3 time} & {\sc synthetic 4 loss} & {\sc synthetic 4 time}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Sparse Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Sparse Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:comparison} Comparison between {\sc SetMargin}
      (orange), {\sc riVOI} (blue), {\sc QI} (green) and {\sc EUS}
      (gray) on the $r=3$ (left) and $r=4$ (right) datasets. Each row
      represents a different distribution for sampling the underlying
      user utility.  The number of iterations is plotted against the
      utility loss (first and third columns) and the cumulative time
      (second and fourth columns). Thick lines indicate median values
      over users, while standard deviations are shown as shaded
      areas.}
\end{figure*}

@@

\begin{figure*}
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
%        \hline
%        \multicolumn{2}{c}{{\sc loss/time per iter.}} &
%        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
%        \multicolumn{4}{c}{{\sc sparse uniform}}
        \\
%        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
%        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
%        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
%        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}

        \includegraphics[width=.25\textwidth]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        \includegraphics[width=.25\textwidth]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        \includegraphics[width=.25\textwidth]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        \includegraphics[width=.25\textwidth]{figures/pc_with_costs_uniform_sparse_per_query_time}
        \\
%        \hline
        % \multicolumn{4}{c}{{\sc sparse normal}}
        % \\
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_loss} &
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_time} &
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_loss} &
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_time}
        % \\
        % \hline
    \end{tabular}
    }
    \caption{\label{fig:pc} Results for {\sc SetMargin} for $k=2$
      (red), $k=3$ (blue) and $k=4$ (green) on the constructive PC
      dataset for the sparse uniform distribution.}
\end{figure*}

>>>>

\begin{figure*}[h!]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3 loss} & {\sc synthetic 3 time} & {\sc synthetic 4 loss} & {\sc synthetic 4 time}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Sparse Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Sparse Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:comparison} Comparison between {\sc SetMargin}
      (orange), {\sc riVOI} (blue), {\sc QI} (green) and {\sc EUS}
      (gray) on the $r=3$ (left) and $r=4$ (right) datasets. Each row
      represents a different sampling distribution for user utility.
      The number of iterations is plotted against the utility loss
      (first and third columns) and the cumulative time (second and
      fourth columns). Thick lines indicate median values over users,
      while standard deviations are shown as shaded areas.}
\end{figure*}

@@

\begin{figure*}
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
%        \hline
%        \multicolumn{2}{c}{{\sc loss/time per iter.}} &
%        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
%        \multicolumn{4}{c}{{\sc sparse uniform}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}

        % \includegraphics[width=..25\textwidth]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        % \includegraphics[width=.25\textwidth]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        % \includegraphics[width=.25\textwidth]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        % \includegraphics[width=.25\textwidth]{figures/pc_with_costs_uniform_sparse_per_query_time}
        \\
%        \hline
        % \multicolumn{4}{c}{{\sc sparse normal}}
        % \\
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_loss} &
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_time} &
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_loss} &
        % \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_time}
        % \\
        % \hline
    \end{tabular}
    }
    \caption{\label{fig:pc} Results for {\sc SetMargin} for $k=2$
      (red), $k=3$ (blue) and $k=4$ (green) on the constructive PC
      dataset for the sparse uniform distribution. Utility loss and
      time are plotted against number of iterations (left)
      and number of queries (right).}
\end{figure*}
